---
title: "Grid Engine and R Cookbook"
author: "Patrick Miller"
date: "11/18/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Initialization

### Connecting to front end machine

See http://wiki.crc.nd.edu/wiki/index.php/CRC_Quick_Start_Guide for connection details.


### Uploading Files 

- Download a file transfer program (e.g. Cyberduck)
- Using Cyber duck, connect to the remote machine by clicking `Add Connection`.
- Drag and drop files.

### Basic Unix Commands

- `ls` list files
- `cd` change directory
- `mkdir` make directory
- `rm` rm file

Use `Tab` to autocomplete files and folder names to esnure accuracy.

Edit the file `.cshrc` to contain the following aliases, replacing `username` with your username. This allows default coloring for folders and files, and creates the commonly used command `qst` for viewing the status of your jobs in the queue.

```
alias ls 'ls --color=auto' 
alias qst 'qstat -u username'
```





### Exercise 1:

- Create a file `ex1.R` with the following:
```{r, eval=FALSE}

f <- function(x){
  x
}
f(1)
```

- Create a directory on the head node called `ex1`
- Upload `ex1.R` to `ex1`

### Running R from the command Line

Software on the crc is available by loading up specific modules. 

`> module avail`

Lists all the available modules.

`> module load R`

Loads R. R programs can be run as scripts using the command `Rscript`

`> Rscript ex1.R`

# Example 1

# Example 2

# Example 3